### 2018-06-01 submission/supplemental.Rmd
make changes to title and abstract
update table titles

# The Influence of Different High Fidelity DNA Polymerase on 16S rRNA Sequencing

@@

**Table S1: ANOVA Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal and Mock Samples**

@@

**Table S2: Tukey Post-Hoc Results of Differences in Number of OTUs between HiFi DNA Polymerases in Fecal and Mock Samples**

@@

**Table S3: Kruskal-Wallis Results of Differences in Error Rate, Sequences with an Error, and Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

@@

**Table S4: Dunn's Post-Hoc Results of Differences in Error Rate, Sequences with an Error, and Chimera Prevalence between HiFi DNA Polymerases in Mock Samples**

>>>>

# Error Introduced into 16S rRNA Gene Sequencing Results Varies by High Fidelity DNA Polymerase Used

@@

**Table S1: ANOVA results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

**Table S2: Tukey post-hoc results of differences in number of OTUs between polymerases in fecal and mock samples**

@@

**Table S3: Kruskal-Wallis results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**

@@

**Table S4: Dunn's Post-Hoc results of differences in error rate, sequences with an error, and chimera prevalence between polymerases in mock samples**
